Software Citation Principles

### 2016-02-11 sc-principles/software-citation-principles.tex
added ref to Google Doc of use cases
minor changes is wording below table 1, also testing sharelatex sync

\begin{table}[htbp]
\caption{Use cases for software citation}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{DOI} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher & someone else's software for a paper	& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & someone else's software for new software& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & contribute to software 				& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & find citations of software 			& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Researcher & credit for software development		& \textbullet & \textbullet &   & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & ``reproduce'' analysis 				& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & benchmark software 					& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & find software to implement task 		& \textbullet & \textbullet &   &   & \textbullet & \textbullet & \textbullet & \\
Publisher & publish software paper					& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Publisher & publish papers that cite software 		& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Indexer & build catalog of software 				& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Domain group & build catalog of software 			& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Library\slash archive & build catalog of software 	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Repository & show scientific impact of holdings 	& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Funder & show how funded software has been used		& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

Meaning of ``researcher'' includes academic researcher (e.g., postdoc, tenure-track faculty member) and research software engineer.
``Reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility.
Examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search.
Domain groups include ASCL, bioCADDIE.

>>>>

\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases}}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{DOI} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher & someone else's software for a paper	& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & someone else's software for new software& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & contribute to software 				& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & find citations of software 			& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Researcher & credit for software development		& \textbullet & \textbullet &   & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & ``reproduce'' analysis 				& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & benchmark software 					& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & find software to implement task 		& \textbullet & \textbullet &   &   & \textbullet & \textbullet & \textbullet & \\
Publisher & publish software paper					& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Publisher & publish papers that cite software 		& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Indexer & build catalog of software 				& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Domain group & build catalog of software 			& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Library\slash archive & build catalog of software 	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Repository & show scientific impact of holdings 	& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Funder & show how funded software has been used		& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

``Researcher'' includes academic researchers (e.g., postdoc, tenure-track faculty member) and research software engineers.
``Reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility.
Examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search.
Domain groups include ASCL, bioCADDIE, CIG, etc.
